\documentclass[11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\begin{document}

{\LARGE \textbf{John Lawrence Darcy, PhD}}\\
Senior Scientist (Bioinformatics)\\
\href{mailto:John.L.Darcy@gmail.com}{John.L.Darcy@gmail.com} $\vert$ 303 887 0477 $\vert$ \href{https://github.com/darcyj}{github.com/darcyj} $\vert$ \href{https://scholar.google.com/citations?user=z24F3PYAAAAJ&hl=en}{Google Scholar}

\vspace{6pt}
\hrule
\vspace{8pt}

\textbf{Summary}\\
Bioinformatician and Biostatistician with 14+ years of experience supporting cross-disciplinary research through development of reproducible analytical pipelines and statistical software for multi-omic datasets (RNA-seq, proteomics, metagenomics). Expertise in R, Python, C++, high-throughput sequencing analysis, and cloud/HPC workflows.

\vspace{4pt}
\textbf{Selected Impact}
\begin{itemize}
  \item Reduced data QA/QC processing turnaround time by 98\% through automated pipelines.
  \item Developed six production R packages, including one commercialized analytical tool.
  \item Improved GSEA algorithm performance (about 1.5x faster, up to 20\% increased power).
  \item Built cloud-native bioinformatics pipelines on AWS for production-scale omics data.
\end{itemize}

\textbf{Professional Experience}

\textbf{Senior Scientist (Bioinformatics), Jonah Ventures} \hfill 04/2025 -- Present
\begin{itemize}
  \item Designed and scaled a cloud-native ONT metabarcoding pipeline (65+ amplicons, AWS).
  \item Led bioinformatics engineering for RNA-baits metagenomic enrichment platform workflows.
  \item Developed reproducible data processing pipelines for environmental DNA workflows.
\end{itemize}

\textbf{Bioinformatics Scientist, Standard BioTools (formerly SomaLogic)} \hfill 10/2021 -- 10/2024
\begin{itemize}
  \item Built R Shiny applications for non-computational scientists.
  \item Designed and deployed an automated QC pipeline reducing turnaround time by 98\%.
  \item Built internal R packages to standardize PHI-compliant workflows.
\end{itemize}

\textbf{NIH NLM Computational Biology Postdoctoral Fellow, CU Anschutz} \hfill 10/2018 -- 10/2021
\begin{itemize}
  \item Developed and published the R package \textit{specificity} (R + C++).
  \item Published a mathematical model for temporal patterns in microbiome data.
\end{itemize}

\textbf{Postdoctoral Researcher (Mycology), University of Hawaii} \hfill 08/2017 -- 10/2018

\textbf{Technical Skills}\\
R (expert), Python, Shell (bash), C++, AWS, HPC, SQL, CI/CD, Git, R Shiny, ggplot2, Plotly.

\textbf{Education}\\
PhD, Ecology and Evolutionary Biology, University of Colorado Boulder (2017)\\
BA, Molecular, Cellular, and Developmental Biology, University of Colorado Boulder (2010)

\vfill
\textbf{Publications:} 44+ peer-reviewed co-authored publications, 9 first-author publications.

\end{document}
